---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgdownreprex

<!-- badges: start -->
[![Title](https://img.shields.io/badge/pkgdown-reprex-green.svg)]()
[![R build status](https://github.com/fmmattioni/pkgdownreprex/workflows/R-CMD-check/badge.svg)](https://github.com/fmmattioni/pkgdownreprex/actions)
<!-- badges: end -->

The goal of `pkgdownreprex` is to test different settings from the `pkgdown` package for rendering the website. It is algo going to be used in case a `reprex` is neeeded to be shared with the developers.

## Package creation workflow:

1. `usethis::create_package()`

1. `usethis::use_mit_license()`

1. `gitignore::gi_fetch_templates(template_name = c("macOS", "R"), copy_to_clipboard = TRUE)`

    1. Pasted it into `.gitignore`

1. `usethis::use_readme_rmd()`

1. `usethis::use_pkgdown()`

1. `usethis::use_vignette("pkgdownreprex")`

1. `usethis::use_git()`

    1. In the terminal: `git remote add origin https://github.com/fmmattioni/pkgdownreprex.git`

1. `usethis::use_github_actions()`

1. `usethis::use_github_action("pkgdown")`

```{r echo = FALSE}
library(usethis)
library(pkgdown)
```

<details><summary>Session info</summary>
```{r}
sessioninfo::session_info()
```
</details>
